\textbf{Response Letter}

### 2018-12-25 doc/aij18/major-revision/experiments.tex
Update Dec 25 21:40

\begin{itemize}
	\item \textbf{\FO action sequence and \PO state trajectory}: This is the common case addressed by most of the state-of-the-art learning approaches, which corresponds to a scenario where the plan horizon is given by the action sequence. In this experiment we assume a degree of observability of only 10\% for the state trajectory, meaning that each literal of a state has a 10\% chance of being observed.
	\item  \textbf{\NO action sequence and \NO state trajectory}: In this case study, both the input action sequence and state trajectory are {\em empty} and the length of the plan is unknown. Only the initial and final states are observed; i.e., $\tau = \tup{s_0, s_m}, \forall \tau \in \mathcal{T}$.
\end{itemize}

Figures \ref{fig:np_quality} and \ref{fig:np_time} show the quality of the models and computation time, respectively, for the first case study. \textcolor{red}{The values plotted in these figures are averages over the 15 domains.} In Figure \ref{fig:np_quality} we see that, after three traces, precision stabilizes at 0.84 whereas recall stabilizes at 0.95. These results show that \FAMA does, in fact, not need big amounts of input knowledge to learn sound and complete models as opposite to other approaches in the literature where models are learned using around 100 traces (see Table \ref{table:models_comparison2}).

@@

Table \ref{tab:results_minimum_100_10} shows the results of the first case study. Recall scores are generally higher than the precision ones, and, in fact, the models learned for six out of the 15 domains were perfectly complete. Although precision is overall lower, it is interesting to notice that the learned sets of negative effects are mostly flawless. With regards to the computation time, we can observe times are below one second in most cases except for some of the more complex domains.

@@

Table \ref{tab:results_minimum_30_30} gathers the results of the case study with 30\% observability.  We can see in the table that the scores of some domains are missing. This is the case of {\em floor-tile} and {\em grid}, which not only are fairly complex domains, but also categorized as \emph{puzzle-like} domains, a feature that is known for putting a strain in the planners. Interestingly enough, we note the high computation time of {\em hanoi} and {\em parking}, which also qualify as a \emph{puzzle-like} domains. Regarding quality, we find that the learned models retain a level of soundness similar to Table~\ref{tab:results_minimum_100_10} but the completeness is lower than in the previous case study. This is specially noticeable in the preconditions, where recall values drop from from 0.88 to 0.64. This is because the input actions act as strong constraints playing a key role on the closeness of the learned model to the GTM. The more actions are missing in the input knowledge, the more likely the occurrence of reformulations.

@@

Table \ref{tab:metric_comparison_100_10} shows the results of the first case study. Looking at the high scores of the syntactic metrics, specially the value of recall, we can conclude that the learned models are, in fact, fairly similar to the GTM. This supports our conclusion that no reformulation occurs in this case study, which also means that the space of possible solutions is restricted to models close to the GTM. The values of sem-Precision and sem-Recall are also very high across the table, which is exactly the desired behavior for these metrics given that solutions are very close to the GTM. In comparison, recall and sem-Recall show similar scores, while sem-Precision is significantly higher than precision, thus showing that the sem-Precision is more lenient towards extra preconditions or effects. This is in line with the results of the previous experiments, where the common appearance of redundant or implicit preconditions in the learned models is penalized by the precision metric. We can interpret this phenomenon as a manifestation of the qualification problem~\cite{GinsbergS88}. For instance, the model learned for the {\tt\small move} action of the {\em hanoi} domain specifies that both the origin and destination disks must be bigger than the one moving, but the GTM contains only one of these preconditions. This learned model is semantically correct but syntactically different from the GTM and hence penalized by the precision metric.

Table~\ref{tab:metric_comparison_0_0} details the results of the \NO/\NO case study. One first observation is the impossibility of applying a semantic evaluation in some of the most complex domains with five traces. Contrary to the previous case study, the difference between the syntactic and semantic metrics is larger in this scenario with unknown plan horizon. Comparing the scores of both versions, we find that learned models that achieved mediocre scores when using the GTM as reference (syntactic metrics), are in fact reasonably sound and complete, reaching overall scores of 0.92 and 0.89 in sem-Precision and sem-Recall. This is an indication that the models learned by our approach, despite syntactically different from the GTM, require very few editions to explain the testing set of traces.

>>>>

\begin{itemize}
	\item \textbf{\FO action sequence and \PO state trajectory (known plan horizon)}: This is the common case addressed by most of the state-of-the-art learning approaches, which corresponds to a scenario where the plan horizon is given by the action sequence. In this experiment we assume a degree of observability of only 10\% for the state trajectory, meaning that each literal of a state has a 10\% chance of being observed.
	\item  \textbf{\NO action sequence and \NO state trajectory (unknown plan horizon)}: In this case study, both the input action sequence and state trajectory are {\em empty} and the length of the plan is unknown. Only the initial and final states are observed; i.e., $\tau = \tup{s_0, s_m}, \forall \tau \in \mathcal{T}$.
\end{itemize}

Figures \ref{fig:np_quality} and \ref{fig:np_time} show the quality of the models and computation time, respectively, for the case \FO/\PO. \textcolor{red}{The values plotted in these figures are averages over the 15 domains.} In Figure \ref{fig:np_quality} we see that, after three traces, precision stabilizes at 0.84 whereas recall stabilizes at 0.95. These results show that \FAMA does, in fact, not need big amounts of input knowledge to learn sound and complete models as opposite to other approaches in the literature where models are learned using around 100 traces (see Table \ref{table:models_comparison2}).

@@

Table \ref{tab:results_minimum_100_10} shows the results of the case study \FO/\PO. Recall scores are generally higher than the precision ones, and, in fact, the models learned for six out of the 15 domains were perfectly complete. Although precision is overall lower, it is interesting to notice that the learned sets of negative effects are mostly flawless. With regards to the computation time, we can observe times are below one second in most cases except for some of the more complex domains.

@@

Table \ref{tab:results_minimum_30_30} gathers the results of the case study \PO/\PO with 30\% observability.  We can see in the table that the scores of some domains are missing. This is the case of {\em floor-tile} and {\em grid}, which not only are fairly complex domains, but also categorized as \emph{puzzle-like} domains, a feature that is known for putting a strain in the planners. Interestingly enough, we note the high computation time of {\em hanoi} and {\em parking}, which also qualify as a \emph{puzzle-like} domains. Regarding quality, we find that the learned models retain a level of soundness similar to Table~\ref{tab:results_minimum_100_10} but the completeness is lower than in the previous case study. This is specially noticeable in the preconditions, where recall values drop from 0.88 to 0.64. This is because the input actions act as strong constraints playing a key role on the closeness of the learned model to the GTM. The more actions are missing in the input knowledge, the more likely the occurrence of reformulations.

@@

Table \ref{tab:metric_comparison_100_10} shows the results of the case study \FO/\PO. Looking at the high scores of the syntactic metrics, specially the value of recall, we can conclude that the learned models are, in fact, fairly similar to the GTM. This supports our conclusion that no reformulation occurs in this case study, which also means that the space of possible solutions is restricted to models close to the GTM. The values of sem-Precision and sem-Recall are also very high across the table, which is exactly the desired behavior for these metrics given that solutions are very close to the GTM. In comparison, recall and sem-Recall show similar scores, while sem-Precision is significantly higher than precision, thus showing that the sem-Precision is more lenient towards extra preconditions or effects. This is in line with the results of the previous experiments, where the common appearance of redundant or implicit preconditions in the learned models is penalized by the precision metric. We can interpret this phenomenon as a manifestation of the qualification problem~\cite{GinsbergS88}. For instance, the model learned for the {\tt\small move} action of the {\em hanoi} domain specifies that both the origin and destination disks must be bigger than the one moving, but the GTM contains only one of these preconditions. This learned model is semantically correct but syntactically different from the GTM and hence penalized by the precision metric.

Table~\ref{tab:metric_comparison_0_0} details the results of the case study \NO/\NO. One first observation is the impossibility of applying a semantic evaluation in some of the most complex domains with five traces. Contrary to the previous case study, the difference between the syntactic and semantic metrics is larger in this scenario with unknown plan horizon. Comparing the scores of both versions, we find that learned models that achieved mediocre scores when using the GTM as reference (syntactic metrics), are in fact reasonably sound and complete, reaching overall scores of 0.92 and 0.89 in sem-Precision and sem-Recall. This is an indication that the models learned by our approach, despite syntactically different from the GTM, require very few editions to explain the testing set of traces.
